Rough Cut of Proven Work on $\SH$.

### 2019-07-23 tex/Rough-Overview.tex
Added code to kernel_ranks to generate matrices for representation
Fixed data
Comments for the kernel proof

\section{Introduction}
Let $S_{2n+r}$ be the symmetric group on $2n+r$ indices with $2n + r \geq 2$, let $\SH = \SH_{k,q}(S_{2n+r})$ be the corresponding Hecke algebra over field $k$ with parameter $q \in k^\times$ having square root $q^{1/2}$, and let $\cbr{T_i}$ be the reflections generating $\SH$.
Let $\brk{m}_q = 1 + q + \dots + q^{m-1}$ be the $q$-number of $m$. 
Let $e$ be the smallest positive integer such that $\brk{e}_q = 0$, and set $e = \infty$ if no such integer exists.
Either $q = 1$ and $e$ is the characteristic of $k$, or $q \neq 1$ and $q$ is a primitive $e$th root of unity.

@@

\begin{equation}
  \begin{split}
  T_1 \, (*pp) &:= \vara(*pp)\\
  T_1 \, (pp*) &:= \vara(pp*)\\
  T_1 \, (*p*) &:= \varb(*p*)\\
  T_1 \, (p*p) &:= \varc(p*p) + \vard(ppp)\\
  T_1 \, (ppp) &:= \vard(p*p) + \vare(ppp)
\end{split} \label{Fib Action} 
\end{equation}
for constants
\begin{equation}
  \begin{split}
  \vara &= -1\\
  \varb &= q\\
  \varc &= \tau(q\tau - 1)\\
  \vard &= \tau^{3/2}(q + 1)\\
  \vare &= \tau(q-\tau)\\
  \tau &= \begin{cases}
    \frac{1}{2}\prn{\sqrt 5 - 1} & \ell \equiv 1,4 \pmod 5\\
    \frac{1}{2}\prn{\sqrt 5 + 1} & \ell \equiv 2,3 \pmod 5
  \end{cases}
\end{split} \label{Fib Constants} 
\end{equation}
with $T_i$ acting similarly on the substring $i,i+1,i+2$.
We will verify that this is a representation of $\SH$ in Appendix \ref{Fib Relations}

This contains 4 subrepresentations based on the first and last character of the string, which are not modified by $\SH$.
Label the subrepresentation of strings $(*\dots*)$ by $V_{**}$, and similar for the other 3.
It is easy to see that $V_{*p} \simeq V_{p*}$, so that
\[
  V \simeq 2V_{*p} \oplus V_{**} \oplus V_{pp}.
\]
We will show that $V_{pp} \simeq V_{*p} \oplus V_{**}$, and give the following isomorphisms with irreducible quotients of specht modules depending on the parity of the number of indices in $\SH$:
\begin{equation}
  \begin{split}    
    F^{2n}_{**} &\simeq D^{(n,n)'}\\ 
    F^{2n-1}_{**} &\simeq D^{(n+1,n-2)'}\\
    F^{2n}_{*p} &\simeq D^{(n+1,n-1)'}\\
    F^{2n-1}_{*p} &\simeq D^{(n,n-1)'}.
  \end{split} \label{Fib Isos}
\end{equation}

@@

\subsection{The Fibonacci Representation} 
\label{Fib Relations}
Similar to before, the reader may verify that \eqref{braid2} follows easily, and the others may be verified on strings of length 3 and 4.
By considering the coefficients in order of \eqref{Fib Action}, the quadratic relation \eqref{quadratic} gives the following quadratics:
\begin{equation}
  \begin{split}
    (\vara - q)(\vara + 1) &= 0\\
    (\varb - q)(\varb + 1) &= 0\\
    \varc\vard + \vard\vare &= (q-1)\vard\\
    \varc^2 + \vard^2 &= (q -1)\varc + q\\
    \vare^2 + \vard^2 &= (q -1)\vare + q
  \end{split}
\end{equation}
The first two of these are easily verified for any $q$.
Since $\vard \neq 0$, the third is equivalently given by
\[
  (q - 1) = \varc + \vare = t(q\tau - 1 + q - \tau) = (\tau^2 + \tau)(q - 1)
\]
or that $\prn{\tau^2 + \tau - 1}(q-1) = 0$.
The reader may verify that $\tau^2 + \tau - 1 = 0$, so this is true for every $q$.

@@

\vspace{7pt}
We now verify \eqref{braid1}.
We may order the basis for $V^4$ as follows:
\[
  \cbr{(pppp),(*pp*),(ppp*),(*ppp),(*p*p),(p*p*),(pp*p),(p*pp)}.
\]
Then, in verifying the braid relation \eqref{braid1} in this order, we encounter the following quadratics (with tautologies and repetitions omitted):
\begin{align*}
    \vara\vare^2 + \varb\vard^2 &= \vara^2 \vare\\
    \vara\vard\vare + \varb\varc\vard &= \vara\varb\vard\\
    \varb\varc^2 + \vara\vard^2 &= \varb^2\varc\\
    \vara\varc^2 + \vard^2\vare &= \vara^2\varc\\
    \vard\vare^2 + \vara\varc\vard &= \vara\vard\vare
\end{align*}
The reader may verify that each of these are satisfied for $q$ a primitive 5th root of unity and $\tau$ as defined.

This highlights the difficulty with deforming our module to $q = 1$ at any field;
the quadratic relations require that $(\tau^2 + \tau - 1)(\tau^2 + \tau + 1) = 0$, but neither of these appear in the first braid relation, which reads $\tau (\tau^3 - 6 \tau^2 + 1) = 0$.
If we have $\tau^2 + \tau \pm 1 = 0$, then $\tau \neq 0$ and $-7\tau^2 \pm \tau + 1 = 0$.
Hence $(7 \pm 1)\tau + (1 \pm 1) = 0$, implying that $\tau = \frac{1}{4},0$, neither of which satisfy $\tau^2 + \tau \pm 1 = 0$, a contradiction.

To attempt to deform this to $q = 1$ would require that we rewrite $\varc,\vard,\vare$ entirely, rather than simply modifying $\tau$.

>>>>

\section{Introduction}
Let $S_{2n+r}$ be the symmetric group on $2n+r$ indices with $2n + r \geq 2$, let $\SH = \SH_{k,q}(S_{2n+r})$ be the corresponding Hecke algebra over field $k$ with parameter $q \in k^\times$ having square root $q^{1/2}$, and let $\cbr{T_i}$ be the reflections generating $\SH$.
Let $\brk{m}_q = 1 + q + \dots + q^{m-1}$ be the $q$-number of $m$. 
Let $e$ be the smallest positive integer such that $\brk{e}_q = 0$, and set $e = \infty$ if no such integer exists.
Either $q = 1$ and $e$ is the characteristic of $k$ (with $0$ replaced by $\infty$), or $q \neq 1$ and $q$ is a primitive $e$th root of unity.

@@

\begin{equation}
  \begin{split}
  T_1 \, (*pp) &:= \vara(*pp)\\
  T_1 \, (pp*) &:= \vara(pp*)\\
  T_1 \, (*p*) &:= \varb(*p*)\\
  T_1 \, (p*p) &:= \varc(p*p) + \vard(ppp)\\
  T_1 \, (ppp) &:= \vard(p*p) + \vare(ppp)
\end{split} \label{Fib Action} 
\end{equation}
for constants
\begin{equation}
  \begin{split}
  \vara &= -1\\
  \varb &= q\\
  \varc &= \tau(q\tau - 1)\\
  \vard &= \tau^{3/2}(q + 1)\\
  \vare &= \tau(q-\tau)\\
  \tau &= -1-q^2-q^3
\end{split} \label{Fib Constants} 
\end{equation}
with $T_i$ acting similarly on the substring $i,i+1,i+2$.
We will verify that this is a representation of $\SH$ in Appendix \ref{Fib Relations}

This contains 4 subrepresentations based on the first and last character of the string, which are not modified by $\SH$.
Label the subrepresentation of strings $(*\dots*)$ by $V_{**}$, and similar for the other 3.
It is easy to see that $V_{*p} \simeq V_{p*}$, so that
\[
  V \simeq 2V_{*p} \oplus V_{**} \oplus V_{pp}.
\]
We will show that $V_{pp} \simeq V_{*p} \oplus V_{**}$, and give the following isomorphisms with irreducible quotients of specht modules depending on the parity of the number of indices in $\SH$:
\begin{equation}
  \begin{split}    
    V^{2n}_{**} &\simeq D^{(n,n)'}\\ 
    V^{2n-1}_{**} &\simeq D^{(n+1,n-2)'}\\
    V^{2n}_{*p} &\simeq D^{(n+1,n-1)'}\\
    V^{2n-1}_{*p} &\simeq D^{(n,n-1)'}.
  \end{split} \label{Fib Isos}
\end{equation}

@@

\subsection{The Fibonacci Representation} 
\label{Fib Relations}
Similar to before, the reader may verify that \eqref{braid2} follows easily, and the others may be verified on strings of length 3 and 4.
By considering the coefficients in order of \eqref{Fib Action}, the quadratic relation \eqref{quadratic} gives the following quadratics:
\begin{equation}
  \begin{split}
    (\vara - q)(\vara + 1) &= 0\\
    (\varb - q)(\varb + 1) &= 0\\
    \varc\vard + \vard\vare &= (q-1)\vard\\
    \varc^2 + \vard^2 &= (q -1)\varc + q\\
    \vare^2 + \vard^2 &= (q -1)\vare + q
  \end{split}
\end{equation}
The first two of these are easily verified for any $q$.
Since $\vard \neq 0$, the third is equivalently given by
\[
  (q - 1) = \varc + \vare = t(q\tau - 1 + q - \tau) = (\tau^2 + \tau)(q - 1)
\]
or that $\prn{\tau^2 + \tau - 1}(q-1) = 0$.
One may verify that \[\tau^2 + \tau - 1 = q^6 + 2q^5 + q^4 + q^3 + q^2 - 1 = (-1+q+q^2)\brk{5}_q = 0.\]

@@

\vspace{7pt}
We now verify \eqref{braid1}.
We may order the basis for $V^4$ as follows:
\[
  \cbr{(pppp),(*pp*),(ppp*),(*ppp),(*p*p),(p*p*),(pp*p),(p*pp)}.
\]
Then, in verifying the braid relation \eqref{braid1} in this order, we encounter the following quadratics (with tautologies and repetitions omitted):
\begin{align*}
    \vara\vare^2 + \varb\vard^2 &= \vara^2 \vare\\
    \vara\vard\vare + \varb\varc\vard &= \vara\varb\vard\\
    \varb\varc^2 + \vara\vard^2 &= \varb^2\varc\\
    \vara\varc^2 + \vard^2\vare &= \vara^2\varc\\
    \vard\vare^2 + \vara\varc\vard &= \vara\vard\vare
\end{align*}
Substituting in $\tau$ and dividing by $\delta$ whenever possible, these are equivalent to the vanishing of the following polynomials in $q$:
\begin{align*}
  -q (1 + q) (1 + q^2 + q^3) (2 + q + 3 q^2 + 2 q^3) \brk{5}_q &= 0\\
  (1 + 2 q + q^3 + q^4) \brk{5}_q &= 0\\
  (1+q)^2 (1+q^2+q^3) (1+3q^3 - q^4 + q^6)\brk{5}_q &= 0\\
  (1+q)^2 (1+q^2+q^3) (1+5q+5q^2+3q^3+3q^4+3q^5+q^6)\brk{5}_q &= 0\\
  (1+q) (1+q^2+q^3) (-1+2q+q^2+q^3+q^4)\brk{5}_q &= 0.
\end{align*}
Notably, each of these vanish when $e = 5$.
